---
title: "whichState"
author: "Gerald Lee"
date: "'r Sys.Date()'"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{whichState}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### The `whichState` package was created to help anyone who wanted to find out which American state a particular phone number or a set of phone numbers are from. This package extracts the first 3 digits of a phone number and matches them to the US directory of Area codes.

### For instance, New York has several Area codes and 212 is one of them.

```{r setup}
library(whichState)
whichState(2121234567, us=TRUE)
```

### The function has 2 arguments, the first is the US 10 digit phone number and the second which is set to default `us=TRUE`. The second argument is set to default because the function will only work for US phone numbers. if the phone numbers are from a different country, the function will not work.
